### 2020-12-20 README.Rmd
attempt 1 for github action (dangerous) - check, covr and pkgdown all in 1

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare)
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare)
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)
[![R-CMD-check](https://github.com/skgallagher/EpiCompare/workflows/R-CMD-check/badge.svg)](https://github.com/skgallagher/EpiCompare/actions)
<!-- badges: end -->
